A Control Strategy for a Tethered Follower Robot for Pulmonary Rehabilitation

### 2020-12-07 alpibot.tex
Subo la información final del paper.

We added on the Webots simulation a 5 kg mass on top of our model, and adjusted the coefficients $c_v$ and $c_{\alpha}$ for the  \textit{Follow the thread}  control strategy.  Results are consistent with the outcomes shown previously on Figures~\ref{fig:simulationresults} and~\ref{fig:realworldresults}.  In Figure~\ref{fig:validationwithtank} it can be seen that the shape of the trajectory follows the patient smoothly, the speed profile also follows stringently the leader speed, and finally the distance between the patient and the robot is maintained within the safe boundaries.  The obtained metrics are 0.2223 for m.t.d. and 1.1068 for t.t.d. which shows that the following behavior is achieved and verifies, from the simulation perspective, the initial feasibility of the control strategy considering the addition of the oxygen tank.

>>>>

We added on the Webots simulation a 5 kg mass on top of our model, and adjusted the coefficients $c_v$ and $c_{\alpha}$ for the  \textit{Follow the thread}  control strategy.  Results are consistent with the outcomes shown previously on Figures~\ref{fig:simulationresults} and~\ref{fig:realworldresults}.  In Figure~\ref{fig:validationwithtank} it can be seen that the shape of the trajectory follows the patient smoothly, the speed profile also follows closely the leader speed, and finally the distance between the patient and the robot is maintained within the safe boundaries.  The obtained metrics are 0.2223 for m.t.d. and 1.1068 for t.t.d. which shows that the following behavior is achieved and verifies, from the simulation perspective, the initial feasibility of the control strategy considering the addition of the oxygen tank.
